### 2024-05-23 chapters/glossary.tex
feat(appendices): update sever description (#14)
* feat(appendices): add server-descripion appendix

* Rename appendix

* Add first page of software installation appendix

* Move to correct page

* feat(main.sty): add sections custom style

* feat(figures): add docker-compose-influxdb.jpg

* feat(server-description): update

* feat(bib): add ssh tunnels ref

* feat(figures): update docker-compose-influxdb image

* feat(appendices): update server-description

* feat(abstracts): add extra line

* chore(style): update section style

* feat(appendices): update server description

\newglossaryentry{log}{
    name=Log,
    description={Registre}
}

>>>>

\newglossaryentry{log}{
    name            = Log,
    description     = {Registre}
}
% TODO: add plural

\newglossaryentry{ssh}{
    name            = ssh,
    description     = {Secure Shell Protocol}
}

\newglossaryentry{OSTIA}{
    name            = OSTIA,
    description     = {Open Science Toolkit Information Access}
}

\newglossaryentry{UPCommons}{
    name            = UPCommons,
    description     = {Portal del coneixement obert de la Universistat Politècnica de Catalunya}
}

\newglossaryentry{OAI}{
    name            = OAI,
    description     = {Open Archives Initiative, normalent associat amb OAI-PMH}
}

\newglossaryentry{OAI-PMH}{
    name            = OAI-PMH,
    description     = {Open Archives Initiative Protocol for Metadata Harvesting}
}

\newglossaryentry{plugin}{
    name            = plugin,
    description     = {Complement, extensió}
}

\newglossaryentry{Docker}{
    name            = Docker,
    description     = {Plataforma per la construcció, execució i desenvolupament d'aplicacions basades en contenidors}
}

\newglossaryentry{docker-compose}{
    name            = docker-compose,
    description     = {Eina per la definició i execució d'aplicacions multi-contenidor}
}

\newglossaryentry{gitignore}{
    name            = gitignore,
    description     = {Al sistema de control de versions Git, especifica els fitxers intencionalment ignorats}
}
